---
title: "Using_github_tutorial"
author: "Tesswin Thomas"
date: "2/15/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---


# Using github - a tutorial 

This document is created to review on how to use git with R studio. 
From this project onwards, all the codes to be synced with github

Some initialization 
- Make sure "create a git repository" is checked when creating a project 
- Pre-requisites 
- Installed version of git in the computer 
- A github account 
- Creation of personal access token in github account via settings/developersettings/personalaccesstoken 
- Storing of this token in r environment 

- before that initialize the library 

```{r installing_packages}
# the library required is "usethis" 

# install.packages("usethis") 
library(usethis)
```

- use the following command to save the personal access token from github to r_environment 

```{r environment_check}
edit_r_environ()
# the copied PAT is stored in R environement as GITHUB_PAT = "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"

# restart R to take the R environment to take effect 
```

- following code to use to connect to github 

```{r}
use_git_config(user.name = "xxx", user.email = "xxx@xxx.com")
```

- Now need to use use_github function to 

```{r}
use_github(protocol = "https", auth_token = Sys.getenv("GITHUB_PAT"))
```

- use the commit from "Git" tab to commit and "push" to push the codes to github repository 
